That's No Moon: New Analysis Shows No Evidence for Lunar Companion Orbiting Kepler-1625b

### 2019-01-17 ms.tex
analysis

We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.  This software has yielded consistent results with multiple independent pipelines \citep[e.g.][]{knutson14b, spake18}.  We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI). The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples. In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude.

@@

We reduced the grism exposures with the optimal extraction routine of \citep{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.  The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.  For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).  We measured and subtracted the background from the data array as described in \ref{sec:background}. For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).  The initial bad pixel mask included pixels marked with the data quality flag 4 or 512 (dead pixels or blobs).

In brief, optimal extraction is an iterative procedure with the following steps. First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 15$.

@@

\section{Analysis}
The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise that is common to WFC3 data \citep{zhou17}. We model the astrophysics and the instrument systematics simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}. In our analysis, we considered two astrophysical scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius, the planet radius, the time of central transit, the planet inclination, and. We used a quadratic limb darkening law and fixed the coefficients to the prediction for FIXME from FIXME.  We also fixed the orbital period to FIXME \citep{teachey18b}. Eccentricity zero, Jupiter mass. Varying this parameters would allow

Host star parameters were estimated using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}. We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters. The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr.

\subsection{Instrument Systematics Model}
There are two systematic trends in the data. One is the orbit-long ramp, attributed to charge traps in the detector filling up over the orbit \citep{zhou17}. The other is a visit-long

. To model the ramp, we use the nonparametric model for the orbit-long hook from \cite{teachey18b}, which is

and a decorrelation

For exposure number $i$, we 
\begin{equation}
S_i = c_{i\Mod9}\times(1 + aX_i + bY_i) 
\end{equation}

\section{Comparison with Teachey \& Kipping (2018)}

>>>>

We reduced the \HST\ data using custom software developed in \cite{kreidberg14a}.  This software has yielded consistent results with multiple independent pipelines \citep[e.g.][]{knutson14b, spake18}.  We ran our pipeline on the \texttt{flt} data product provided by the Space Telescope Science Institute (STScI). The \texttt{flt} files are corrected for dark current, bias, and nonlinearity, and they are cleaned of cosmic ray hits based on a fit to the up-the-ramp samples. In keeping with previous WFC3 analysis, we discarded the first orbit of data, where the instrument systematics have larger amplitude. We also discard exposures taken during the South Atlantic Anomaly passage (exposures 107, 116, 125, and 126).

@@

We reduced the grism exposures with the optimal extraction routine of \cite{horne86}, which minimizes background noise in the extracted spectrum by weighting pixels that are dominated by the target spectrum more heavily than pixels dominated by the background.  The inputs for optimal extraction are the background-subtracted data array, the error array (including photon noise read noise, and uncertainty due to background subtraction), an initial guess for the spectrum and its uncertainty, and a mask array for bad pixels.  For the initial guess of the spectrum and its uncertainty, we did a simple box extraction (sum over all rows in the extraction window), and assumed the variance was equal to the box-extracted spectrum (expected for photon noise limit).  We measured and subtracted the background from the data array as described in \ref{sec:background}. For the error array, we used a quadrature sum of the photon noise (the square root of the pixel counts), the read noise (12 photoelectrons for \texttt{flt} files; WFC3 Data Handbook\footnote{\url{http://www.stsci.edu/hst/wfc3/documents/handbooks/currentDHB/}}), and the error due to background subtraction (described in \ref{sec:background}).  The initial bad pixel mask included pixels marked with the data quality flag 4 or 512 (dead pixels or blobs).

In brief, optimal extraction is an iterative procedure with the following steps. First, we created a smoothed image by median-filtering each row of the data with a 9-pixel-wide window.  We then normalized the smoothed image by dividing each column by its sum, and multiplied it by the best guess spectrum. We compared the smoothed image to the real data and masked outliers in the data that are greater than a threshold $\sigma_\mathrm{cut}$. We then recomputed the best guess spectrum with the new mask and the optimal weights from \cite{horne86}. The process is iterated until no outliers greater than the threshold remain.  This procedure masks any cosmic rays or bad pixels that were missed by the initial \texttt{flt} calibration.  We tested a range of thresholds ($4 < \sigma_\mathrm{cut} < 15$) and found that different $\sigma_\mathrm{cut}$ choices did not significantly change the final transit light curve. The data reported in this work use $\sigma_\mathrm{cut} = 15$.  To create the braodband transit light curve, we sum each spectrum over all wavelengths.

@@

\section{Analysis}
The raw light transit light curve (shown in Figure~\ref{fig:raw}) contains both astrophysical signal and instrument systematic noise, which we model simultaneously.

\subsection{Astrophysics Model}
For the astrophysics, we used the \texttt{planetplanet} package \citep{luger17}, a photodynamical code that calculates light curves for multiple occulting bodies orbiting a star. Within \texttt{planetplanet}, the orbits are computed with the N-body integrator \texttt{REBOUND} \citep{rein??}. In our analysis, we considered two scenarios: a no-moon model and a moon model. The free parameters for the no-moon model were: the stellar radius $R_*$, the planet radius $R_\mathrm{planet}$, the time of central transit $t_\mathrm{planet}$, and the planet inclination $i$. For the moon model, we added a third body with radius $R_\mathrm{moon}$, transit time $t_\mathrm{moon}$, and orbital period $P_\mathrm{moon}$. We fixed the inclination of the moon to $90^\circ$ to exclude grazing transit scenarios, where the moon radius could be arbitrarily large.  We also fixed the moon mass and eccentricity to zero.  We fixed the planet's orbital period to 287.378949 days \citep{teachey18b}. For both the moon and no-mooon models, we fixed the planet eccentricity to zero and the mass to $1\,M_\mathrm{Jup}$. The \texttt{planetplanet} model uses these input parameters and returns the relative system flux for each exposure.

\subsubsection{Stellar Parameters}
For both the moon and no-moon scenarios, we used a quadratic stellar limb darkening law and fixed the coefficients to the prediction for a 5700~K, solar metallicity \texttt{PHOENIX} model from \cite{espinoza15}; $u_1, u_2 = [0.216, 0.183]$.

We estimated the host star parameters using the Gaia DR2 parallax \citep{Gaia, GaiaDR2} along with UBV photometry from \citet{Everett2012} and JHK photometry from 2MASS \citep{2MASS}. We employed the isochrone python package \citep{isochrone} with the Dartmouth isochrone grid \citep{Dotter2008} to obtain posterior constraints on the stellar parameters. The resulting parameters indicate that Kepler-1625 has stellar mass $1.37^{+0.13}_{-0.16}$ M$_{\odot}$, radius $1.81^{+0.18}_{-0.16}$ R$_{\odot}$, and age $2.8^{+1.6}_{-1.2}$ Gyr. In our analysis, we fixed the stellar mass to the best fit value ($1.37\,M_\odot$), and used a Gaussian prior on the radius, $R_* \sim N(1.81, 0.17)$.

\subsection{Instrument Systematics Model}
There are two systematic trends in the data. One is the orbit-long ramp, attributed to charge traps in the detector filling up over the orbit \citep{zhou17}. The other is a visit-long trend over multiple orbits, which could be due to shifts in the target star position onto more/less sensitive pixels.

To fit the orbit-long ramp, we used the non-parametric model from \cite{teachey18b}, which assigns each of the nine exposures per orbit a normalization constant, $c_1, ..., c_9$. To fit the visit-long trend, we used a linear combination of $X$ and $Y$ position (the shift relative to the mean in the spatial and spectral directions, respectively; shown in Figure~\ref{fig:shifts}).  In sum, for exposure number $i$, the systematics model is:
\begin{equation}
S_i = c_{j}\times(1 + aX_i + bY_i) 
\end{equation}
where $a$ and $b$, and $c_j$ are free parameters, and $j = i\Mod9 + 1$ is the exposure number relative to the first exposure in the orbit.

We also considered a second, more complex systematics model, $S_2$, which added a visit-long quadratic trend. A long-term trend was favored by the \cite{teachey18b} analysis, and has been observed in other long-duration WFC3 time series \citep[e.g.][]{stevenson14, kreidberg18b}. The model is:
\begin{equation}
S_{2,i} = c_{j}\times(1 + aX_i + bY_i) \times (1 + vt_i + v_2t_i^2)
\end{equation}
where $v$ and $v_2$ are free parameters and $t_i$ is the time elapsed since the first exposure in the visit.

\subsection{Light Curve Fits}
We fit the raw, broadband transit light curve using the models described above.  For comparison, we also fit the raw light curve from \cite{teachey18b}.  In total, we fit each data set with four different models:

\begin{enumerate}
\item{No moon, non-parametric ramp, X-Y decorrelation} 
\item{Moon, non-parametric ramp, X-Y decorrelation} 
\item{No moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
\item{Moon, non-parametric ramp, X-Y decorrelation, visit-long polynomial} 
\end{enumerate}

For each model, we determined the best fit parameters with least-squares minimization.  We also ran a Markov chain Monte Carlo (MCMC) fit to determine the posterior probability of each parameters. The MCMC used the \texttt{emcee} package \citep{foremanmackey13} with 50 walkers and ran for $10^4$ steps.

\section{Results}
Figure FIXME shows the best fits.
